Regional and Urban Economics

### 2023-02-19 Retail Agglomeration_Theory.qmd
Add files via upload
Har laget nytt dokument med Teori hadde problemer med å merge... Forslag her.

Our main task in this assignment is to perform an analysis of geo-spatial determinants of firm activity.
More specifically we are to focus on the Norwegian dental industry in this regard, and see how geo-spatial determinants such as distances to shopping malls and CBDs (Central Business Districts), as well as population density can determine dental businesses income and general financial operations.
As an example, central questions in this assignment will be; "Is it more beneficial to be highly centralized in urban areas with high population density and many competitors, or is it a greater advantage to be less centralized to the advantage that the nearest competing company is considerably further away?", "Which determinants appear to be most significant for economic benefit?"

@@

## Literature Review

#### Previous literature on Shopping malls

### Theoretical Framework

@@

@@

```{r}
NOR_CBD <- read_csv("NOR_CBD.csv")
Dist_CBD_Dentist <- read_csv("Dist_CBD_Dentist.csv")
Buffer_CBD <- read_csv("Buffer_CBD.csv")
Dist_Mal_Dentist <- read.csv("Dist_Mal_Dentist.csv")
NOR_OSM_SHOP_MAL <- read.csv("NOR_OSM_SHOP_MAL.csv")
Buffer_den <- read.csv("Buffer_den.csv")
NOR_KOMM <- read_csv("NOR_KOMM.csv")
NOR_KOMM_2 <- read_csv("NOR_KOMM_2.csv")
```

```{r}
Commune_Data <- inner_join(NOR_KOMM, NOR_KOMM_2, by = "kommunenummer") |>
  select(kommunenummer, HubName, HubDist, Turnover_capita_retail_Omsetning)
```

```{r}
Dentist_Data <- inner_join(Dist_Mal_Dentist, Dist_CBD_Dentist, by = "fid") |>
  select(fid, Juridisk.n, Antall.ans, Sum.Drifts, Sum.salgsi, Driftsresu.y, osm_id.y, latlong.y, HubName.y, HubDist.y, HubName.x, HubDist.x) |>
  rename("DistMal" = HubDist.x, "DistCBD" = HubDist.y, "HubNameMal" = HubName.x, "HubNameCBD" = HubName.y)
```

```{r}
kable(summary(Commune_Data))
View(commune_data)
```

```{r}
kable(summary(Dentist_Data[3:6]))
```

```{r}
kable(summary(Dentist_Data[8:12]))
```

```{r}
Commune_Data |>
  ggplot(aes(x = DistMal, y = Turnover_capita_retail, colour = DistMal)) +
  geom_point(lwd = .9) +
  labs(x = "Distance from Mall", y = "Turnover capita in retail per inhabitant") +
  theme_bw()
```

```{r}
Dentist_Data |>
  ggplot(aes(x = DistCBD, y = Sum.salgsi, colour = DistCBD)) +
  geom_point(lwd = .9) +
  labs(x = "Distance from CBD", y = "Income") +
  theme_bw()
```

```{r}
Dentist_Data_LIMIT <- Dentist_Data |>
  filter(Sum.salgsi < 100000000, DistCBD < 250,
         Driftsres < 20000000, Driftsres > -10000000, DistMal < 80)
```

```{r}
Dentist_Data_LIMIT |>
  ggplot(aes(x = DistCBD, y = Sum.salgsi, colour = DistCBD)) +
  geom_point(lwd = .9) + labs(x = "Distance from CBD", y = "Income") +
  theme_bw()
```

```{r}
Dentist_Data |>
  ggplot(aes(x = DistMal, y = Driftsres, colour = DistMal)) +
  geom_point(lwd = .9) +
  labs(x = "Distance from Mall", y = "EBIT") +
  theme_bw()
```

```{r}
Dentist_Data_LIMIT |>
  ggplot(aes(x = DistMal, y = Driftsres, colour = DistMal)) +
  geom_point(lwd = .9) +
  labs(x = "Distance from Mall", y = "EBIT") +
  theme_bw()
```

@@

**Econometric Approach**

@@

## Results

## Discussion

@@

## Acknowledgements

>>>>

Our main task in this assignment is to perform an analysis of geospatial determinants of firm activity.
More specifically we are to focus on the Norwegian dental industry in this regard, and see how geospatial determinants such as distances to shopping malls and CBDs (Central Business Districts), as well as population density can determine dental businesses income and general financial operations.
As an example, central questions in this assignment will be; "Is it more beneficial to be highly centralized in urban areas with high population density and many competitors, or is it a greater advantage to be less centralized to the advantage that the nearest competing company is considerably further away?", "Which determinants appear to be most significant for economic benefit?"

@@

## Theoretical Framework

@@

Keynesian economics also emphasizes the importance of consumer demand in driving economic growth.
In regional economics, this may involve policies that involve consumer spending, such as incentives for buying local products or supporting small businesses or in this case preventing the the death of down town due to competition from shopping malls.
Subsequently, By increasing consumer demand, supporting business in a specific region and promoting economic growth or preventing economic decline @capello2016.

@@

@@

## **Econometric Approach**

@@

@@
